### 2014-08-31 fundamentals/intro.tex
modular arch."

\Cyclus separates the problem of modeling a
physics-dependent supply chain into a simulation kernel and archetypes that
interact with the kernel during a simulation. The kernel is responsible for the
deployment and interaction logic of entities in the simulation. Physics
calculations are constrained to individual archetypes. Accordingly, specialists
in a given field can utilize their time and resources in modeling a specific
process associated with the nuclear fuel cycle, e.g. reprocessing and advance
fuel fabrication, rather than also modeling the entirety of the cycle.

% we could use a specific example of Cosi's equivalence method below
Because \Cyclus uses a modular archetype approach, comparing two archetypes is
straightforward. Consider a case in which an analyst would like to compare the
effect of using different models to determining input fuel composition for fast
reactors. A variety fuel fabrication archetypes can be developed and used
interchangably to analyze the effect of each on a simulation's output.

@@

Draw from and cite the ``Open Architecture and Modular Paradigm'' ANS summary.

@@

\begin{figure}[htbp!]
\begin{center}
\includegraphics{./images/modifiedopen.eps}
\end{center}
\caption{The \Cyclus framework enables fully open, partially open, and fully 
closed collaborations.}
\label{fig:modifiedopen}
\end{figure}

>>>>

\Cyclus separates the problem of modeling a
physics-dependent supply chain into a simulation kernel and archetypes that
interact with the kernel during a simulation. The kernel is responsible for the
deployment and interaction logic of entities in the simulation. Physics
calculations are constrained to individual archetypes. Accordingly, specialists
in a given field can utilize their time and resources in modeling a specific
process associated with the nuclear fuel cycle (e.g., reprocessing and advanced
fuel fabrication), rather than also modeling the entirety of the cycle.

@@

The encapsulated plug-in architecture within the \Cyclus tool allows developers 
to define nuclear fuel cycle facility processes independent of the simulation 
logic. This design choice acheives two things. First, analysts across 
institutions can take advantage of the simulation logic \gls{API} and 
archetype ecosystem when they apply \Cyclus to their specific problem. The effort they 
undertake can thereby be focused on creating or customizing 
nuclear facility, institution, resource, and toolkit models within their 
specific area of expertise.

% we could use a specific example of Cosi's equivalence method below
Second, because \Cyclus uses a modular archetype approach, comparing two 
archetypes is straightforward. Consider a case in which an analyst would like 
to compare the effect of using different models to determining input fuel 
composition for fast reactors. A variety fuel fabrication archetypes can be 
developed and used interchangably to analyze the effect of each on a 
simulation's output.

@@
